% Notes
% - Local snippets in ./snips:
%   - (\)chap(tertoc)
%   - (\)rec(ipe)
%   - (\)ere(cipe)
% - Custom Commands:
%   - \chapterrec{title}       - usual chapter meant to have a fore-text
%   - \chaptertoc{title}       - chapter with table of contents
%   - \recipe{title}           - custom section command
%   - \erecipe{title}{source}  - external recipe, adds ToC entry
%   - \itemNL                  - item without label
%   - \namepageref[<s>]{label} - "<name><s><pg>" sep defaults to " on page "
%   - \degF, \about            - cooking shorthand
% - Custom Environments:
%   - ingredients, timeline, directions, directions1col [<alt title>]
%   - IT [<col ratio>]  (ingredients/timeline in 2 column)
%   - twocols
%   - ingredientslist, timelinelist, directionslist, recipelist [enumitem options]
% - How to use the index:
%   - \index{simple entry}
%   - \index{category!entry}          - category,\\  entry
%   - \index{entry!|see{other entry}} - entry ... /see/ other entry
%
% TODO:
% - 

\documentclass[oneside]{book}  % {{{1
\usepackage{lmodern, microtype}              % margins, fonts, etc
\usepackage[T1]{fontenc}                     % ""
\usepackage{calc, etoolbox, nameref, xspace} % utilities
\usepackage{booktabs, enumitem}              % typesetting
\usepackage{datetime2}                       % use YYYY-MM-DD for \today
\usepackage{hyperref}                        % pdf links
\usepackage{amsmath}                         % misc math

% spacing
\usepackage[margin=1in]{geometry}
\setlength{\parskip}{0.5em}

\usepackage{chappg}  % page numbering by chapter: <chapter #>-<page #>

% headers and footers
\usepackage{fancyhdr}
\fancypagestyle{plain}{  % redefine the plain pagestyle
  % Clear all headers and footers, show the date at the top right, and show
  % chapter name, recipe name, and page number on the bottom of the page.
  \fancyhf{}
  \fancyhead[R]{\scriptsize\today}
  \fancyfoot[L]{\leftmark\thisrecipe} \fancyfoot[R]{\thepage}
  % double-sided
  % \fancyhead[RE]{\scriptsize\today}
  % \fancyfoot[LE]{\leftmark\thisrecipe} \fancyfoot[RE]{\thepage}
  % \fancyhead[LO]{\scriptsize\today}
  % \fancyfoot[LO]{\thepage}             \fancyfoot[RO]{\leftmark\thisrecipe}
}
\renewcommand{\headrulewidth}{0em}               % remove header rule
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}  % don't show chapter number
\pagestyle{plain}

% chapters, sections, etc, and ToC (NB: displaying numbers is disabled)
\usepackage{titlesec, titletoc}
\titleformat{\chapter}[display]{\normalfont\bf\Huge}{}{0em}{}
\titlespacing{\chapter}{0em}{-6em}{0em}
\titleformat{\section}{\normalfont\bf\Large}{}{0em}{}[\titlerule]
\pretocmd{\section}{\clearpage}{}{}  % start sections on a new page
\titleformat{\subsection}{\normalfont\bf\large}{}{0em}{}
\titlespacing{\subsection}{0em}{\parskip}{0em}
\titlecontents{chapter}[0em]{\addvspace{1em}\bf}{}{}{~\titlerule*[0.5em]{·}~\contentspage}
\titlecontents{section}[1.5em]{}{}{}{~\titlerule*[0.5em]{·}~\contentspage}
% chapter ToCs: style the sections the same as the chapters (styled above)
\titlecontents{chapter_toc_section}[0em]{\addvspace{1em}\bf}{}{}{~\titlerule*[0.5em]{·}~\contentspage}
% ugly hack: footer normal case, consistent spacing with chapter titles
\renewcommand{\contentsname}{\vspace{1.25em}\NoCaseChange{Contents}}
\setcounter{tocdepth}{1}  % don't show subsections and below in ToC

% custom commands for chapters of recipes and recipes
\def\thisrecipe{}  % initialization
\newcommand{\chapterrec}[1]{  % recipe chapter
  \newpage \def\thisrecipe{} \chapter{#1} \vspace{1.1em}
}
\newcommand{\chaptertoc}[1]{  % recipe chapter with table of contents
  \chapterrec{#1} \vspace{-1.1em}  % make spacing consistent
  \startcontents[chapters] \printcontents[chapters]{chapter_toc_}{1}[1]{}
}
\newcommand{\recipe}[1]{\section{#1}\def\thisrecipe{: #1}} % recipe section
\usepackage{xcolor}  % for \colorbox below
\NewDocumentCommand{\ExternalToCEntry}{mm}{\addtocontents{toc}{\protecting{%
  \contentsline{section}
  {\numberline{}#1}
  {\hspace{-\linewidth}\colorbox{white}{#2}\hspace{-0.3em}}  % \colorbox and negative \hspace are hacks to prevent overfull hboxes and the \dotfill from going through the page number
  {}
} } }
\NewDocumentCommand{\erecipe}{mm}{\ExternalToCEntry{#1}{#2}}  % external recipe

% index
\usepackage{imakeidx}
\makeindex[
  intoc,
  % ugly hack: footer normal case, consistent spacing with chapter titles
  title={\texorpdfstring{\vspace{1.25em}\NoCaseChange{Index}\vspace{0.4em}}{Index}},
  options=-s my-index,
]

% lists
\renewcommand*{\arraystretch}{1.25}
\setlist[enumerate]{itemsep=0.5em}
\setlist[itemize]{itemsep=0.5em}
\setlist[description]{itemsep=0.5em}
\newlist{kitchennotes}{description}{1}
\setlist[kitchennotes]{style=nextline, font=\bfseries, leftmargin=\parindent}
\newlist{kitchensubnoteslist}{itemize}{1}
\setlist[kitchensubnoteslist]{
  font=\bfseries, label=\textbullet, leftmargin=1em, itemsep=0em, topsep=0.5em
}
\NewDocumentEnvironment{kitchensubnotes}{o}
  {
    \phantom{.} \vspace{-2em}
    \IfNoValueTF{#1}{\begin{kitchensubnoteslist}}{\begin{kitchensubnoteslist}[#1]}
  }
  {
    \end{kitchensubnoteslist}
  }
\newlist{ingredientslist}{enumerate}{1}
\newlist{timelinelist}{enumerate}{1}
\newlist{directionslist}{enumerate}{1}
\newlist{recipelist}{enumerate}{1}
\SetEnumitemKey{recipelistStyle}{
  label=\arabic*., font=\bfseries, wide=\parindent, parsep=\parskip,
  topsep=\parskip, labelindent=\parindent,
}
\SetEnumitemKey{ITStyle}{itemsep=0em, label={}, leftmargin=*}
\setlist[ingredientslist]{recipelistStyle, ITStyle}
\setlist[timelinelist]{recipelistStyle, ITStyle}
\setlist[directionslist]{recipelistStyle, itemsep=\parskip}
\setlist[recipelist]{recipelistStyle}
\newcommand{\itemNL}{\item[] \hspace{-\labelsep}}  % item with no label

% custom commands
\renewcommand{\epsilon}{\varepsilon}
\renewcommand{\phi}{\varphi}
\NewDocumentCommand{\todo}{o}{\textbf{ToDo\IfNoValueF{#1}{: #1}}}
\NewDocumentCommand{\namepageref}{O{ on page }m}{\nameref{#2}#1\pageref{#2}}
\newcommand{\degF}{\textdegree F\xspace}
\newcommand{\about}{$\sim$}

% custom environments
\usepackage{multicol, paracol}  % multicolumn environments
\setlength{\multicolsep}{\parskip}
\NewDocumentEnvironment{twocols}{}  % shortcut for \begin{multicols}{2} ...
  {\begin{multicols}{2} \raggedcolumns}{\end{multicols}}
\NewDocumentEnvironment{IT}{O{0.844}}  %  [<col ratio>], ingredients/timeline
  {\columnratio{#1} \begin{paracol}{2}}{\end{paracol}}
\NewDocumentEnvironment{ingredients}{O{Ingredients}}
  {\subsection{#1} \begin{ingredientslist}}
  {\end{ingredientslist}}
\NewDocumentEnvironment{timeline}{O{Timeline}}
  {\subsection{#1} \begin{timelinelist}}
  {\end{timelinelist}}
\NewDocumentEnvironment{directions}{O{Directions}}
  {
    \vspace{-\parskip} \subsection{#1}
    \begin{twocols} \begin{directionslist}
  } {
    \end{directionslist} \end{twocols}
  }
\NewDocumentEnvironment{directions1col}{O{Directions}}
  {\subsection{#1} \begin{directionslist}}
  {\end{directionslist}}

% sources
\NewDocumentCommand{\esource}{mo}{#1\IfNoValueF{#2}{ p#2}\xspace}
\NewDocumentCommand{\CICookbook}{o}{\esource{CI Cookbook}[#1]}
\NewDocumentCommand{\CIMeat}{o}{\esource{CI Meat Book}[#1]}
\NewDocumentCommand{\CIBaking}{o}{\esource{CI Baking Book}[#1]}
\NewDocumentCommand{\CIScience}{o}{\esource{CI Science}[#1]}
\NewDocumentCommand{\InvIndianCooking}{o}{\esource{Inv.\ to Indian Cooking}[#1]}
\NewDocumentCommand{\ATKThirty}{o}{\esource{ATK 30-min}[#1]}
%----------------------------------------------------------------------------}}}1

\begin{document}
\frontmatter \pagenumbering[C]{bychapter} \tableofcontents

\mainmatter

\chapterrec{Notes} \label{chap:notes} % {{{1
\begin{kitchennotes}[font=\MakeUppercase]
  \item[Baking Sheets]
    Use LEGO blocks to build spacers for stacking cookie sheets.

  \item[Bulk Mixed Drinks]
    Pre-mix the drink and put it in the freezer. Make a pitcher of ice water and
    put it in the refrigerator. Work out correct ratio of drink to water (2:1 is
    a good starting point). Combine at time of serving.

  \item[Ginger]
    In many recipes that call for chopped ginger, peeling is not necessary.

  \item[Non-stick Pans]
    Use vegetable oil spray (e.g.\ PAM) on a steel pan. The emulsifiers make the
    pan essentially non-stick.

  \item[Potatoes] \begin{kitchensubnotes}
    \item Boursin cheese can be used to make mashed potatoes. Add a package, use
      less butter, and use milk instead of cream.
    \item Cut potatoes can be stored in water for up to one day.
  \end{kitchensubnotes}
\end{kitchennotes}
%----------------------------------------------------------------------------}}}1

\chapterrec{Sous Vide} \label{chap:sous_vide} % {{{1
\index{sous vide}
\begin{kitchennotes}
  \item[Chicken, Poached]
    \index{Poached Chicken} \index{sous vide!Poached Chicken} \index{chicken!Poached Chicken}
    Cook at 150\degF for at least 2 hours.

  \item[Eggs, Soft Boiled]
    \index{Soft Boiled Eggs} \index{sous vide!Yogurt} \index{eggs!Soft Boiled}
    Heat water to 190\degF and add eggs using spoon. Cook for 9--10 minutes,
    then place in cold water bath.

  \item[Yogurt]
    \index{Yogurt} \index{sous vide!Yogurt}
    Pasteurize the milk for 1 hour at 185\degF. Cool in a water bath to
    115\degF, about 15 minutes. Add yogurt starter and cultivate at 115\degF
    for 4 hours. Strain with colander and coffee filter for 3 hrs.
\end{kitchennotes}
%----------------------------------------------------------------------------}}}1

\chaptertoc{Appetizers} \label{chap:appetizers}
\recipe{Beef Tartare} \label{recipe:beef_tartare} % {{{1
\index{beef!Beef Tartare}

\begin{IT}
  \begin{ingredients}
    \item[1/2 lb] beef sirloin or chuck
    \item[2 Tbsp] olive oil
    \item[1 Tbsp] whole grain mustard
    \item[1 tsp] Dijon mustard
    \item[1] shallot, diced
    \item[1 Tbsp] capers, drained and diced
    \item[1 tsp] Worcestershire sauce
    \item[1 tsp] red wine vinegar
    \item[1] egg yolk
    \itemNL salt and pepper, to taste
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:20
    \item[Cook:]  00:00
    \item[Total:] 00:20
  \end{timeline}
\end{IT}

\begin{directions}
  \item Place the meat grinder, serving bowl, and beef in freezer for 15
    minutes.
  \item Combine all ingredients except the beef in third smallest metal bowl.
    Grind beef and combine. Serve in frozen serving bowl.
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Crab Cakes}{\CICookbook[450]} % {{{1
\index{Crab Cakes|see{\CICookbook[450]}}
\index{crab!Crab Cakes|see{\CICookbook[450]}}
%---------------------------------------------------------------------------}}}1

\chaptertoc{Dinners (with leftovers)} \label{chap:dinners_with_leftovers}
\erecipe{Bolognese Sauce}{\CICookbook[193]} % {{{1
\index{Bolognese Sauce|see{\CICookbook[193]}}
\index{pasta!Bolognese Sauce|see{\CICookbook[193]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Brisket}{\CIMeat[127]} % {{{1
\index{Brisket|see{\CIMeat[127]}}
\index{beef!Brisket|see{\CIMeat[127]}}
%---------------------------------------------------------------------------}}}1
\recipe{Chili} \label{recipe:chili} % {{{1
\index{Chili}
\index{beef!Chili}

\begin{IT}
  \begin{ingredients}
    \item[2] onions, diced
    \item[3] Carolina Reaper peppers
    \itemNL spicy peppers, diced
    \item[2 lbs] ground beef
    \item[2 Tbsp] cumin
    \item[1 Tbsp] chili powder
    \item[4 cans] green chilies
    \item[4 cans] kidney beans
    \item[2 cans] black beans
    \item[4 cans] diced tomatoes
    \item[1 can] tomato sauce
    \item[1 bag] frozen corn
    \itemNL salt and pepper, to taste
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:30
    \item[Cook:]  3:30
    \item[Total:] 4:00
  \end{timeline}
\end{IT}

\begin{directions}
  \item Saut\'e the onions. Once onion is softened, cook diced chilies and
    spices for \about 1 minute. Brown the ground beef.

  \item Combine all remaining ingredients except corn and black beans in large
    pot. Bring to boil, then reduce heat to bare simmer. Cook for 2--3 hours
    until desired texture and consistency is reached.

  \item Add black beans and corn and cook for 1 hour.
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Meatloaf}{\CICookbook[391]} % {{{1
\index{Meatloaf|see{\CICookbook[391]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Pesto}{\CICookbook[161]} % {{{1
\index{Pesto|see{\CICookbook[161]}}
\index{pasta!Pesto|see{\CICookbook[161]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Pork Roast}{\textit{see} \namepageref[ ]{notes:dinners_leftovers}}
\erecipe{Pulled Pork}{\CIMeat[244]} % {{{1
\index{Pulled Pork|see{\CIMeat[244]}}
\index{pork!Pulled Pork|see{\CIMeat[244]}}
%---------------------------------------------------------------------------}}}1
\recipe{Punjabi Meat Curry} \label{recipe:punjabi_meat_curry} % {{{1
\index{Punjabi Meat Curry}
\index{curry!Punjabi Meat Curry}
\index{beef!Punjabi Meat Curry}
\index{goat!Punjabi Meat Curry}

\begin{IT}
  \begin{ingredients}
    \item[5 lbs] red meat (e.g.\ goat or beef)
    \item[1/2 cup] olive oil
    \item[1 tsp] cumin seeds
    \item[2] green cardamom seeds, crushed
    \item[1] bay leaf
    \item[3] yellow onions, minced finely
    \item[3 Tbsp] ginger, chopped
    \item[6] cloves garlic, minced
    \item[4] chili peppers (e.g.\ Serrano)
    \item[3] Carolina reaper peppers
    \item[2 tsp] paprika powder
    \item[1 Tbsp] turmeric powder
    \item[1 Tbsp] chili powder
    \item[1 Tbsp] coriander powder
    \item[3 cans] tomato sauce (1 large can, 1 smaller)
    \item[8--10 cups] chicken broth or water
    \item[2 tsp] garam masala
    \itemNL cilantro
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:30
    \item[Cook:]  3:00
    \item[Total:] 3:30
  \end{timeline}
\end{IT}

\begin{directions}
  \item Heat oil in a pot over medium high heat until shimmering. Add the cumin
  seeds, cardamom and bay leaf and saut\'e for 1 minute, stirring to prevent the
  spices from burning. Add the onion and saut\'e until the onion begins to turn
  light brown.

  \item Add the ginger, garlic and chilies, stirring to prevent burning, and
  cook 2 to 3 minutes. Add the meat and cook until all sides are browned, 10
  to 15 minutes.

  \item Add the paprika, turmeric, red chili powder, and coriander powder. Stir
  well and then add the tomato sauce. Stir and add the water. Increase the heat
  to high and bring the curry to a boil. Reduce the heat to medium-low and
  continue to simmer until the meat is tender.

  \item Once the meat is tender and the liquid has reduced, add garam masala.
  Garnish with chopped cilantro leaves and serve.
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Red Beans and Rice}{\CICookbook[239]} % {{{1
\index{Red Beans and Rice|see{\CICookbook[239]}}
\index{beans!Red Beans and Rice|see{\CICookbook[239]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Roast Beef}{\CIMeat[105]} % {{{1
\index{Roast Beef|see{\CIMeat[105]}}
\index{beef!Roast Beef|see{\CIMeat[105]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Roast Leg of Lamb}{\textit{see} \namepageref[ ]{notes:dinners_leftovers}}
\erecipe{Smothered Pork Chops}{\CIMeat[203]} % {{{1
\index{Smothered Pork Chops|see{\CIMeat[203]}}
\index{pork!Smothered Pork Chops|see{\CIMeat[203]}}
%---------------------------------------------------------------------------}}}1
\recipe{Sopa Seca de Fideos} \label{recipe:sopa_seca_de_fideos} % {{{1
\index{Sopa Seca de Fideos}

\begin{IT}
  \begin{ingredients}
    \item[5 lbs] tomatoes
    \item[8] garlic cloves, unpeeled
    \item[12 oz] chorizo sausage
    \item[20 oz] fideo noodles
    \item[2 cans] chilies in adobo
    \item[2] Carolina reaper peppers
    \item[2 tsp] dried oregano
    \item[1 tsp] black pepper
    \item[2 cups] beef broth
    \item[4] zucchini, diced
    \item[1/2 cup] queso anejo or Parmesan, finely grated 
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  01:00
    \item[Cook:]  00:30
    \item[Total:] 01:30
  \end{timeline}
\end{IT}

\begin{directions}
  \item Roast unpeeled garlic on skillet, turning occasionally until soft, about
    15 minutes.

  \item Broil 3 lbs of the tomatoes on baking sheet \about 4 inches below boiler
    until blackened on one side, about 6 minutes. Flip and broil until other
    side is blackened. Cool and peel.

  \item Pour 6 Tbsp of oil into skillet and heat. When quite hot, place nests in
    oil and fry until browned, about 1 minute. Flip and brown the other side.
    Transfer to a paper towel lined tray and repeat (adding additional oil)
    until all nests are browned.

  \item Brown chorizo and set aside.

  \item Core and dice the remaining 2 lbs tomatoes. Dice the zucchini.

  \item Process broiled tomatoes (incl.\ collected juices), garlic, and chilies
    until pureed.

  \item Heat 1 Tbsp oil in large pot used for chorizo and add tomato puree. Add
    salt and sear over high heat for 10 minutes. Add the broth, oregano, black
    pepper, and diced tomatoes. Vigorously simmer for 10 minutes.

  \item Add the noodles. After 2 minutes, pull the nests apart. Add the zucchini
    and chorizo and cook an additional 2 minutes. Remove from heat and stir in
    the cheese.
\end{directions}
%---------------------------------------------------------------------------}}}1
\recipe{Thanksgiving} \label{recipe:thanksgiving} % {{{1
\index{Thanksgiving}
\index{turkey!Thanksgiving}

\subsection{Sides}
\begin{twocols} \begin{ingredientslist}
  \item apple salad (p\pageref{recipe:apple_salad})
  \item biscuits$^{\dagger \text{ (c.f.\ note)}}$ (p\pageref{recipe:baking_powder_biscuits})
  \item cranberry relish$^\dagger$ (p\pageref{recipe:cranberry_relish})
  \item cornbread dressing$^{\dagger \text{ (c.f.\ note)}}$
  \item green beans or asparagus
  \item mashed potatoes (p\pageref{recipe:mashed_potatoes})
  \item pumpkin pie$^\dagger$ (\CICookbook[720])
  \item sweet potato casserole$^{\dagger \text{ (c.f.\ note)}}$ (\todo)
  \item butternut squash (p\pageref{recipe:butternut_squash})
\end{ingredientslist} \end{twocols}
\noindent $\dagger$: can be made a day prior

\subsection{Notes}
\begin{twocols} \begin{kitchennotes}
  \item[Turkey] \begin{kitchensubnotes}
    \item Brine the day before in the morning. Use 1.5 cups of salt. Dry out and
      leave overnight in the refrigerator.
    \item \todo[slash the skin to produce more drippings?] Lift drumstick and
      cut 1 inch slit in skin where drumstick and thigh meet. Turn turkey on
      side so breast faces down and cut 1 inch slit in skin where top of thigh
      meets breast.
    \item Roast at 275\degF using convection, rotating every hour, until breast
      is 160\degF and thigh is 170\degF, \about 3 hours.
  \end{kitchensubnotes}

  \item[Gravy] \begin{kitchensubnotes}
    \item See \namepageref{recipe:pan_sauces}.
    \item 1.5 cups of fat \emph{should} be enough.
    \item Use 6 qt stock pot.
  \end{kitchensubnotes}

  \item[Sweet Potatoes]
  Can be roasted the day prior in deep tray.

  \item[Miscellaneous]
    \begin{kitchensubnotes}
      \item Biscuits: dough can be made the day prior and refrigerated. Thaw for
        \about 30 minutes prior to baking.
      \item Dressing: cornbread can be made the day before
      \item Dressing: cook for 00:45-1:00 at 375\degF
      \item Dressing and sweet potatoes can be cooked at the same time.
    \end{kitchensubnotes}
\end{kitchennotes} \end{twocols}
%---------------------------------------------------------------------------}}}1
\erecipe{Vodka Cream Sauce (for pasta)}{\ATKThirty[160]} % {{{1
\index{Vodka Cream Sauce (for pasta)|see{\ATKThirty[160]}}
\index{pasta!Vodka Cream Sauce (for pasta)|see{\ATKThirty[160]}}
%---------------------------------------------------------------------------}}}1
\recipe{Notes} \label{notes:dinners_leftovers} % {{{1
\begin{kitchennotes}
  \item[Pork Roast] \index{Pork Roast} \index{pork!Pork Roast}
    Use pork shoulder or pork butt. Score fat cap and use a rub from
    \namepageref{recipe:rubs_for_roasts}. Roast at 325\degF convection for
    \about 5 hours, until roast registers 190\degF. See also \CICookbook[418].
  \item[Leg of Lamb] \index{Leg of Lamb} \index{lamb!Leg of Lamb}
    Score fat cap and use a rub from \namepageref{recipe:rubs_for_roasts}. Roast
    at 325\degF convection until done --- 125\degF, about 1.5 hours. Rest 15
    minutes before carving.
\end{kitchennotes}
%---------------------------------------------------------------------------}}}1

\chaptertoc{Dinners (standalone)} \label{chap:dinners_standalone}
\erecipe{BBQ Chicken}{NA} % {{{1
\index{BBQ Chicken}
\index{chicken!BBQ Chicken}
%---------------------------------------------------------------------------}}}1
\recipe{Chicken Kebabs} \label{recipe:chicken_kebabs} % {{{1
\index{Chicken Kebabs}
\index{chicken!Chicken Kebabs}

\begin{IT}[0.813]
  \begin{ingredients}[Ingredients (yields 4 skewers)]
    \item[1/4 cup] tomato paste
    \item[3 Tbsp] vegetable oil
    \item[2 Tbsp] fish sauce
    \item[3] garlic cloves, grated
    \item[1.5 tsp] sugar
    \item[1 tsp] kosher salt
    \item[1 Tbsp] hot sauce
    \item[2 lbs] boneless skinless chicken thighs, cut into 1-inch pieces
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]     00:45
    \item[Marinate:] 1:00
    \item[Cook:]     00:15
    \item[Total:]    2:00
  \end{timeline}
\end{IT}

\begin{directions}
  \item Whisk tomato paste, vegetable oil, fish sauce, garlic, sugar, salt, and
  hot sauce in large bowl. Add chicken to bowl and toss to coat. Cover and
  marinate for 1-12 hours.

  \item Heat grill for 15 minutes. While grill is heating, thread the chicken
  pieces on to the skewers. Lower heat to medium-high, and cook the kebabs,
  turning every 5 minutes. Cook until meat registers 175\degF, about 15 minutes.
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Chicken Thighs}{NA} % {{{1
\index{Chicken Thighs}
\index{chicken!Chicken Thighs}
%---------------------------------------------------------------------------}}}1
\recipe{Curry Roasted Chicken Drumsticks} \label{recipe:curry_roasted_chicken_drumsticks} % {{{1
\index{Curry Roasted Chicken Drumsticks}
\index{chicken!Curry Roasted Chicken Drumsticks}

\begin{IT}
  \begin{ingredients}
    \item[2.5 lbs] chicken drumsticks
    \item[4 tsp] curry powder
    \item[1 Tbsp] kosher salt
    \item[1.25 tsp] ground cardamom
    \item[1.25 tsp] brown sugar
    \item[3/4 tsp] ground ginger
    \item[3/4 tsp] ground nutmeg
    \item[3/4 tsp] smoked paprika
    \item[2 Tbsp + 1 tsp] warm water
    \item[2 Tbsp + 1 tsp] olive oil
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:45
    \item[Cook:]  1:00
    \item[Total:] 1:45
  \end{timeline}
\end{IT}

\begin{directions}
  \item Adjust oven rack to upper-middle position and heat over to 350\degF.
    Line rimmed baking sheet with aluminum foil and set wire rack in sheet.

  \item Whisk curry powder, salt, cardamom, sugar, ginger, nutmeg, and paprika
    together in small bowl. Add water and oil and stir. Let sit until thickened
    into a paste, 2--3 minutes.

  \item Pat drumsticks dry and brush spice slurry on all sides. Place skin side
    up on wire rack.

  \item Roast until drumsticks register 180\degF, 45--50 minutes, rotating
    sheet halfway through. Turn on broiler and continue to cook until drumsticks
    are well-browned in spots, 2--3 minutes longer. Remove from oven and let
    rest for 10 minutes.

  \item Meanwhile, prepare the herbed yogurt sauce below.
\end{directions}

\smallskip

\begin{twocols}
  \begin{ingredients}[Herbed Yogurt Ingredients]
    \item[1 cup] plain Greek yogurt
    \item[1/2 cup] cilantro, minced
    \item[3 Tbsp] lime juice (1--2 limes)
    \item[2 Tbsp] water
    \item[1/2 tsp] fresh ginger, grated
    \item[1/2 tsp] honey
  \end{ingredients}

  \columnbreak

  \begin{directions1col}[Herbed Yogurt Directions]
  \item Whisk all ingredients in a bowl until smooth. If necessary, add up to 2
    Tbsp additional water so that the sauce is pourable. Season with salt to
    taste and refrigerate.
  \end{directions1col}
\end{twocols}
%---------------------------------------------------------------------------}}}1
\erecipe{Fried Chicken}{\CIMeat[404]} % {{{1
\index{Fried Chicken|see{\CIMeat[404]}}
\index{chicken!Fried Chicken|see{\CIMeat[404]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Hot Dogs and Hamburgers}{\textit{see} \namepageref[ ]{notes:dinners_standalone}}
\recipe{Indian Eggs} \label{recipe:indian_eggs} % {{{1
\index{Indian Eggs}
\index{eggs!Indian Eggs}

\begin{IT}
  \begin{ingredients}
    \itemNL oil
    \item[2 tsp] cumin seeds
    \item[2 small] onions, sliced
    \itemNL hot peppers
    \item[3 in.\ piece] ginger, coarsely chopped
    \item[6 cloves] garlic
    \item[2 tsp] turmeric
    \item[1/2 tsp] ground cumin
    \item[2 tsp] chili powder
    \item[1/2 tsp] black pepper
    \item[5] eggs
    \item[2] tomatoes (optional)
    \itemNL red cabbage (optional)
    \item[1/2 tsp] garam masala
    \itemNL salt to taste
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  \todo
    \item[Cook:]  \todo
    \item[Total:] \todo
  \end{timeline}
\end{IT}

\begin{directions}
  \item Heat oil in a pot over medium high heat until shimmering. Add the cumin
  seeds and saut\'e for 2 minutes until the seeds change color, stirring to
  prevent the spices from burning.

  \item Reduce heat to medium and add the onion, saut\'eing until the onion
  begins to turn light brown. Add the hot peppers, ginger, garlic, turmeric,
  ground cumin, chili powder, and black pepper, stirring frequently to prevent
  burning, and cook 2 to 3 minutes until quite fragrant.

  \item Add the tomatoes (if using), then the eggs,  and continue cooking until
  done. Off heat, add garam masala and salt.
\end{directions}

\todo[Tomatoes and red cabbage?]
%---------------------------------------------------------------------------}}}1
\erecipe{Pan-Seared Salmon}{\CICookbook[443]} % {{{1
\index{Pan-Seared Salmon|see{\CICookbook[443]}}
\index{fish!Pan-Seared Salmon|see{\CICookbook[443]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Pan-Seared Shrimp}{\CICookbook[455]} % {{{1
\index{Pan-Seared Shrimp|see{\CICookbook[455]}}
\index{shrimp!Pan-Seared Shrimp|see{\CICookbook[455]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Pan-Seared Thin Fish}{\textit{see} \namepageref[ ]{notes:dinners_standalone}}
\erecipe{Red Sauce (for pasta)}{\ATKThirty[157]} % {{{1
\index{Red Sauce (for pasta)|see{\ATKThirty[157]}}
\index{pasta!Red Sauce (for pasta)|see{\ATKThirty[157]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Shrimp Scampi}{\CICookbook[455]} % {{{1
\index{Shrimp Scampi|see{\CICookbook[455]}}
\index{shrimp!Shrimp Scampi|see{\CICookbook[455]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Steak}{\textit{see} \namepageref[ ]{notes:dinners_standalone}}
\erecipe{Tacos}{\textit{see} \namepageref[ ]{notes:dinners_standalone}}
\recipe{Vietnamese Braised Chicken} \label{recipe:vietnamese_braised_chicken} % {{{1
\index{Vietnamese Braised Chicken}
\index{chicken!Vietnamese Braised Chicken}

\begin{IT}
  \begin{ingredients}
    \item[2 lbs] chicken thighs, bone-in, skin-on
    \item[3 inches] ginger, cut into matchsticks
    \item[1] shallot, sliced thin
    \item[2] garlic cloves, sliced thin
    \itemNL hot peppers, to taste (e.g.\ 8), sliced thin
    \item[4 tsp] sugar
    \item[2 tsp] vegetable oil
    \item[1.5 cups] chicken broth
    \item[2 Tbsp] fish sauce
    \item[1 Tbsp] cornstarch
    \itemNL cilantro, coarsely chopped
    \item[1.5 cups] rice
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:30
    \item[Cook:]  01:00
    \item[Total:] 01:30
  \end{timeline}
\end{IT}

\begin{directions}
  \item Place chicken thighs skin-down on cutting board. Trim excess fat and
    skin and de-bone. Keeping as much skin as possible, cut into 1.5 inch
    pieces.

  \item Scatter sugar evenly in bottom of medium saucepan. Add oil and do not
    stir. Cook on medium-high heat without stirring until sugar becomes the
    color of honey, 2--3 minutes. Reduce heat to medium-low, and cook until
    bubbles form and sugar is the color of soy sauce, stirring frequently, about
    1 minute.

  \item Immediately add the ginger, shallot, and garlic and increase the heat to
    medium-high. Cook, stirring frequently, until aromatic, about 30 seconds.
    Add the chicken and cook, stirring frequently, until no longer pink. Add the
    sliced peppers.

  \item Add the chicken broth and the fish sauce. Bring to a boil, then reduce
    heat and simmer until reduced by half, 25--30 minutes. At this point, begin
    cooking the rice and prepping any other sides.

  \item Make a slurry with the cornstarch and some of the braising liquid and
    add back to the pot. Off heat add the chopped cilantro and soy sauce to
    taste.
\end{directions}
%---------------------------------------------------------------------------}}}1
\recipe{Notes} \label{notes:dinners_standalone} % {{{1
\begin{kitchennotes}
  \item[Hot Dogs and Hamburgers] \label{recipe:hot_dogs_and_hamburgers}
    \index{Hot Dogs and Hamburgers} \index{beef!Hamburgers}
    For 1 lb of meat, use 1 packet of Lipton's French Onion Soup mix and 1 Tbsp
    of Worcestershire sauce.
  \item[Pan-Seared Thin Fish] \label{recipe:pan-seared_thin_fish}
    \index{Pan-Seared Thin Fish} \index{fish!Pan-Seared Thin Fish}
    Thoroughly dry the fish, then dredge \emph{only one side} in mixture of
    flour (2 Tbsp), salt (1/2 tsp), and pepper (1/4 tsp). Cook flour-side down
    in pan for \about 2 minutes, then remove from heat, flip the fish, and
    continue to cook for 15-30 seconds until opaque.
  \item[Steak] \label{recipe:steak}
    \index{Steak} \index{beef!Steak}
    Cook on high heat, turning every minute, for 5--6 minutes.
  \item[Tacos] \label{recipe:tacos}
    \index{Tacos} \index{beef!Tacos}
    Get a seasoning with cornstarch or flour in it. 1 lb ground beef is enough
    for 2-3 people.
\end{kitchennotes}
%---------------------------------------------------------------------------}}}1

\chaptertoc{Sides} \label{chap:sides}
\recipe{Agrodolce Pearl Onions and Shallots} \label{recipe:agrodolce_pearl_onions_and_shallots} % {{{1
\index{Agrodolce Pearl Onions and Shallots}

\begin{IT}
  \begin{ingredients}
    \item[1 c] water
    \item[1/2 tsp] salt
    \item[1/8 tsp] baking soda
    \item[1 lb] frozen pearl onions
    \item[8 oz] small shallots

    \item[1 Tbsp + 1/2 c] white wine vinegar
    \item[2 Tbsp] brown sugar
    \item[2 Tbsp] raisins
    \item[1/4 tsp] black pepper
    \item[3 Tbsp] butter, cut into 3 pieces
    \item[4] scallions, green parts only, cut into 1-inch pieces
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:15
    \item[Cook:]  00:20
    \item[Total:] 00:30
  \end{timeline}
\end{IT}

\begin{directions}
  \item Combine water, salt, and baking soda in 12-inch skillet and bring to a
  boil. Add pearl onions and shallots and return to a boil. Add 1 Tbsp white
  wine vinegar, reduce heat to medium, and cook for 12-15 minutes until most
  liquid has evaporated.

  \item Uncover and add vinegar, sugar, raisins and pepper. Increase heat to
  high and continue cooking until liquid has thickened to the consistency of
  heavy cream, 4-6 minutes.

  \item Off heat, add butter and scallion greens. Serve one butter is melted.
\end{directions}
%---------------------------------------------------------------------------}}}1
\recipe{Apple Salad} \label{recipe:apple_salad} % {{{1
\index{Apple Salad}
\index{salad!Apple Salad}

\begin{IT}
  \begin{ingredients}[Ingredients (yields 4 servings)]
  \item[2] apples, 1 granny smith and 1 sweet
  \item[2 oz] cheddar cheese, sharp
  \item[1/4 cup] raisins or craisins
  \item[1/4 cup] walnuts or pecans, chopped
  \item[1 stalk] celery
  \item[3/4 cups] plain yogurt
  \item[1/2 Tbsp] brown sugar
  \item[1/2 Tbsp] lemon juice
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:30
    \item[Total:] 00:30
  \end{timeline}
\end{IT}

\begin{directions}
  \item Cut all ingredients into bite-sized pieces. Leave apple skin on if
  desired.

  \item Prepare the dressing. Mix brown sugar with lemon juice until fully
  dissolved, then add to yogurt. Taste using an apple cube and add additional
  lemon or sugar if needed.

  \item Combine all ingredients.
\end{directions}
%---------------------------------------------------------------------------}}}1
\recipe{Asian Pasta Salad} \label{recipe:asian_pasta_salad} % {{{1
\index{Asian Pasta Salad}
\index{pasta!Asian Pasta Salad} \index{salad!Asian Pasta Salad}

\begin{IT}
  \begin{ingredients}
    \item[8 oz] pasta
    \item[8 oz] frozen edamame
    \item[11 oz] green coleslaw mix
    \item[4] green onions, white parts chopped, green parts sliced thin
    \item[1/3 cup] chopped ginger
    \item[1/3 cup] rice vinegar
    \item[1.5 Tbsp] hot sauce
    \item[2 tsp] toasted sesame oil
    \item[1.5 tsp] salt
    \item[1/2 cup] vegetable oil
    \item[2 tsp] toasted black sesame seeds
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:30
    \item[Cook:]  00:15
    \item[Total:] 00:45
  \end{timeline}
\end{IT}

\begin{directions}
  \item Boil water and add pasta, cooking until al dente. Add edamame a cook 2
  minutes more. Drain and rinse with cold water. Add coleslaw mix and the green
  parts of the green onion, stirring to combine.

  \item Add green onion whites, ginger, vinegar, hot sauce, sesame oil, and salt
  to blender and blend until coarse paste forms, \about 30 seconds. Add oil
  and blend until dressing is emulsified and smooth, \about 1 minute.

  \item Toss dressing with salad. Sprinkle sesame seeds in while tossing.
\end{directions}
%---------------------------------------------------------------------------}}}1
\recipe{Butternut Squash} \label{recipe:butternut_squash} % {{{1
\index{Butternut Squash}

\begin{IT}
  \begin{ingredients}
    \item[3/4 cup] apple cider or juice
    \item[3/4 cup] water
    \item[1 Tbsp] maple syrup
    \item[1 Tbsp] Dijon mustard
    \item[1 Tbsp] soy sauce
    \item[1/4 tsp] pepper
    \item[1/8 tsp] baking soda
    \item[3 Tbsp] butter
    \item[1] shallot, halved and sliced thin
    \item[2.5 lbs] butternut squash
    \item[1/4 cup] dried cranberries, chopped
    \item[2 Tbsp] apple cider vinegar
    \item[1/2 tsp] fresh rosemary, chopped
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:20
    \item[Cook:]  00:35
    \item[Total:] 00:55
  \end{timeline}
\end{IT}

\begin{directions}
  \item Peel the squash, making sure to entirely remove fibrous white layer,
  then seed and cut into 1 inch pieces.

  \item Whisk together cider, water, maple syrup, mustard, soy sauce, pepper,
  and baking soda and set aside.

  \item Melt butter in 12-inch skillet over medium heat. Add shallot and cook
  until slightly browned, \about 5 minutes.

  \item Stir in squash, add cider mixture, increase heat to high, and bring to a
  simmer. Cover and reduce heat to medium. Simmer until tender and the sauce is
  reduced to the thickness of heavy cream, \about 20-25 minutes, adding the
  chopped cranberries halfway through cooking.

  \item Off heat, stir in the rosemary and cider.
\end{directions}
%---------------------------------------------------------------------------}}}1
\recipe{Classic Pasta Salad} \label{recipe:classic_pasta_salad} % {{{1
\index{Classic Pasta Salad}
\index{pasta!Classic Pasta Salad} \index{salad!Classic Pasta Salad}

\begin{IT}
  \begin{ingredients}
    \item[8 oz] pasta
    \item[1 lb] broccoli crowns, cut into bite-size pieces
    \item[1 can] cannellini beans
    \item[3/4 tsp] salt
    \item[1/4 cup + 1/4 cup] jarred banana peppers
    \item[1/4 cup] banana pepper brine
    \item[1/4 cup + 1/4 cup] Castelvetrano olives, pitted
    \item[2] garlic cloves
    \item[1/2 cup] olive oil
    \item[10 oz] cherry tomatoes, halved
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:45
    \item[Cook:]  00:00
    \item[Total:] 00:45
  \end{timeline}
\end{IT}

\begin{directions}
  \item Line baking sheet with paper towels. Boil water and add pasta, cooking
  until tender, about 5 minutes. Add broccoli and beans and cook until tender,
  1-2 minutes. Drain and spread on prepared baking sheet.

  \item Combine 1/4 cup peppers, brine, 1/4 cup olives, garlic, and salt in
  blender until coarse paste forms, \about 30 seconds. Add oil and continue to
  blend until dressing is emulsified and smooth.

  \item Combine pasta mixture, tomatoes, 1/4 cup banana peppers (chopped), 1/4
  cup olives (quartered), and dressing. Toss to coat.
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Coleslaw}{\CICookbook[57]} % {{{1
\index{Coleslaw|see{\CICookbook[57]}}
%---------------------------------------------------------------------------}}}1
\recipe{Cranberry Relish} \label{recipe:cranberry_relish} % {{{1
\index{Cranberry Relish}

\begin{IT}
  \begin{ingredients}
    \item[1/4 cup] sugar
    \item[1] clementine, unpeeled, stemmed and quartered
    \item[12 oz (3 cups)] frozen cranberries, thawed
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]   00:10
    \item[Chill:]  1:00
    \item[Total:]  1:10
  \end{timeline}
\end{IT}

\begin{directions}
  \item Process sugar and clementine in food processor until clementine is
  finely ground, scraping the bowl as needed, about 20 seconds.

  \item Add cranberries and pulse until berries are chopped into pea-sized
  pieces, about 15-20 pulses.

  \item Transfer to bowl and refrigerate for at least 1 hour, or up to 24 hours.
  Stir to recombine.
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Cucumber Salad}{\CICookbook[45]} % {{{1
\index{Cucumber Salad|see{\CICookbook[45]}}
\index{salad!Cucumber Salad|see{\CICookbook[45]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Hummus}{\CICookbook[8]} % {{{1
\index{Hummus|see{\CICookbook[8]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Indian Carrots, Potatoes, Peas}{\InvIndianCooking[156]} % {{{1
\index{Indian Carrots, Potatoes, Peas|see{\InvIndianCooking[156]}}
\index{category!Indian Carrots, Potatoes, Peas|see{\InvIndianCooking[156]}}
%---------------------------------------------------------------------------}}}1
%\recipe{Indian Cauliflower} \label{recipe:indian_cauliflower} % {{{1
%\index{Indian Cauliflower}
%\index{cauliflower!Indian Cauliflower}

%\begin{IT}
%  \begin{ingredients}
%  \item \vspace{15em}
%  \end{ingredients}

%  \switchcolumn

%  \begin{timeline}
%    \item[Prep:]
%    \item[Cook:]
%    \item[Total:]
%  \end{timeline}
%\end{IT}

%\begin{directions}
%  \item
%  % \columnbreak
%\end{directions}
%%---------------------------------------------------------------------------}}}1
\erecipe{Indian Green Beans with Mustard}{\InvIndianCooking[152]} % {{{1
\index{Indian Green Beans with Mustard|see{\InvIndianCooking[152]}}
\index{green beans!Indian Green Beans with Mustard|see{\InvIndianCooking[152]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Mashed Potatoes}{see \namepageref[ ]{notes:sides}}
\recipe{Mashed Sweet Potatoes} \label{recipe:mashed_sweet_potatoes} % {{{1
\index{Mashed Sweet Potatoes}
\index{sweet potatoes!Mashed Sweet Potatoes}

\begin{IT}
  \begin{ingredients}
    \item[2 lbs] sweet potatoes, peeled and cut into 1/2-inch pieces
    \item[3 Tbsp] butter, cut into 1/2-inch pieces
    \item[1/4 tsp] salt
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:05
    \item[Cook:]  00:25
    \item[Total:] 00:30
  \end{timeline}
\end{IT}

\begin{directions}
  \item Bring 6 cups of water to boil in large saucepan over high heat. Add
  sweet potatoes, return to a boil, cover, reduce heat to medium-low to simmer,
  and cook until fork pierces potatoes with little resistance, about 12 minutes.

  \item Drain potatoes and cook over medium heat, stirring frequently, for 7
  minutes, adjusting heat to prevent excessive browning (steam should be
  steadily escaping).

  \item Off heat, add butter and salt. Whisk until butter is fully incorporated.
  Season with salt to taste.
\end{directions}
%---------------------------------------------------------------------------}}}1
\recipe{Pan Seared Zucchini} \label{recipe:pan_seared_zucchini} % {{{1
\index{Pan Seared Zucchini}
\index{zucchini!Pan Seared Zucchini}

\begin{IT}
  \begin{ingredients}
    \item[2] zucchini, halved lengthwise
    \item[2 tsp] salt
    \item[3 Tbsp] vegetable oil
    \item[1 Tbsp] honey
    \item[1 Tbsp] hot sauce
    \item[1] green onion, sliced thin
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:30
    \item[Cook:]  00:15
    \item[Total:] 00:45
  \end{timeline}
\end{IT}

\begin{directions}
  \item Lightly score the flesh of the zucchini diagonally, then score again on
  the opposite diagonal to create a crosshatched scoring pattern. Sprinkle salt
  over the zucchini and rub into the cuts. Place zucchini cut-side down on
  paper-towel lined plate. Microwave zucchini for 3 minutes, then cut each in
  half.

  \item Put oil in cold non-stick pan, arrange zucchini cut-side down in pan,
  and cover. Heat on medium-high heat until deeply browned, 8-10 minutes.

  \item Uncover and turn zucchini cut-side up and continue cooking until tender,
  about 2 minutes. Transfer cut-side up to paper towel lined plate and let drain
  for \about 5 minutes.

  \item Meanwhile, mix honey and hot sauce and microwave for \about 30 seconds.
  Drizzle honey mixture over zucchini, sprinkle with scallions, and serve.
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Potato Salad}{\CICookbook[59]} % {{{1
\index{Potato Salad|see{\CICookbook[59]}}
\index{salad!Potato Salad|see{\CICookbook[59]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Rice Pilaf}{\CICookbook[222]} % {{{1
\index{Rice Pilaf|see{\CICookbook[222]}}
\index{rice!Rice Pilaf|see{\CICookbook[222]}}
%---------------------------------------------------------------------------}}}1
\recipe{Salmorejo (chilled tomato soup)} \label{recipe:salmorejo} % {{{1
\index{Salmorejo}
\index{soup!Salmorejo} \index{tomatoes!Salmorejo}

\begin{IT}
  \begin{ingredients}
    \item[3 lbs] ripe tomatoes, cored and quartered
    \item[6 oz] white bread, crust removed
    \item[1 Tbsp] red wine vinegar
    \item[1 tsp] salt
    \item[1/4 tsp] garlic, grated
    \item[1/4 cup + 1/4 cup] olive oil
    \item[2] eggs, hard boiled, chopped fine
    \item[2 oz] prosciutto, cut into 1-inch pieces
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:25
    \item[Rest:]  2:00
    \item[Total:] 00:25
  \end{timeline}
\end{IT}

\begin{directions}
  \item Process tomatoes in blender until smooth, \about 30 seconds. Strain
  through sieve over large bowl, using a rubber spatula to press through.

  \item Add bread, vinegar, salt, and garlic to tomato puree and toss to
  combine.

  \item Blend half of the tomato mixture until smooth, \about 2-3 minutes. Add
  1/4 cup oil and blend \about 15 seconds. Do no overblend! Repeat with
  remaining half of tomato mixture. Cover and refrigerate for at least 2 hours.

  \item To serve, garnish with chopped hard boiled eggs and prosciutto,
  drizzling with a little olive oil.
\end{directions}
%---------------------------------------------------------------------------}}}1
\recipe{Notes} \label{notes:sides} % {{{1
\begin{kitchennotes}
  \item[Cornbread Dressing] \label{recipe:cornbread_dressing}
    \index{Cornbread Dressing}
    Cook 3 packages of Jiffy Corn Muffin mix in most shallow tray the day prior.
    Combine with saut\'eed and seasoned onions, carrots, and celery, chicken
    broth (don't use too much!), and 3 eggs. Cook at 375\degF for \about 1 hour.
  \item[Mashed Potatoes] \label{recipe:mashed_potatoes}
    \index{Mashed Potatoes} \index{potatoes!Mashed Potatoes}
    Cut potatoes can be left in water for up to 1 day.
    \todo
\end{kitchennotes}
%---------------------------------------------------------------------------}}}1

\chaptertoc{Breakfast} \label{chap:breakfast}
\erecipe{French Toast}{\CICookbook[551]} % {{{1
\index{French Toast|see{\CICookbook[551]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Lemon Blueberry Pancakes}{\CIBaking[87]} % {{{1
\index{Lemon Blueberry Pancakes|see{\CIBaking[87]}}
\index{pancakes!Lemon Blueberry Pancakes|see{\CIBaking[87]}}
%---------------------------------------------------------------------------}}}1

\chaptertoc{Baked Goods} \label{chap:baked_goods}
\erecipe{Apple Pie}{\CICookbook[713]} % {{{1
\index{Apple Pie|see{\CICookbook[713]}}
\index{pie!Apple Pie|see{\CICookbook[713]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Angel Food Cake}{\CIBaking[270]} % {{{1
\index{Angel Food Cake|see{\CIBaking[270]}}
\index{cake!Angel Food Cake|see{\CIBaking[270]}}
%---------------------------------------------------------------------------}}}1
\recipe{Baking Powder Biscuits} \label{recipe:baking_powder_biscuits} % {{{1
\index{Baking Powder Biscuits}
\index{biscuits!Baking Powder Biscuits}

\begin{IT}
  \begin{ingredients}[Ingredients (yields 4 biscuits)]
    \item[180 g] flour
    \item[1/2 tsp] salt
    \item[1/2 Tbsp] baking powder
    \item[1/2 Tbsp] sugar
    \item[3 Tbsp] butter, \textbf{room temperature}
    \item[118 g] milk
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:20
    \item[Cook:]  00:20
    \item[Total:] 00:40
  \end{timeline}
\end{IT}

\begin{directions}
  \item Preheat oven to 425\degF.

  \item Mix flour, salt, baking powder, and sugar in food processor.

  \item Add butter to processor and process until mixture has a sandy
  consistency.

  \item Slowly add milk to running processor until a cohesive dough forms. If
  dough seems dry, add additional milk.

  \item Roll out the dough on a floured work surface with floured rolling pin,
  folding and rolling repeatedly. Form dough into 3/4 inch disc.

  \item Cut dough into biscuits and place biscuits onto baking sheet. Brush tops
  of biscuits with milk, and place in oven for 15--20 minutes until lightly
  browned. (For 4 biscuits, 18 minutes is about the right time.)
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Banana Bread}{\CIBaking[27]} % {{{1
\index{Banana Bread|see{\CIBaking[27]}}
\index{bread!Banana Bread|see{\CIBaking[27]}}
%---------------------------------------------------------------------------}}}1
\recipe{Banana Muffins} \label{recipe:banana_muffins} % {{{1
\index{Banana Muffins}
\index{muffins!Banana Muffins}

\begin{IT}
  \begin{ingredients}
    \item[5] very ripe (i.e.\ black) bananas
    \item[100 g] sugar \todo[can this be reduced to 75?]
    \item[2] eggs
    \item[1/3 cup] vegetable oil
    \item[1 Tbsp] vanilla extract
    \item[260 g] bread flour
    \item[1 Tbsp] baking powder
    \item[1/2 tsp] baking soda
    \item[1/2 tsp] salt
    \item[1/3 cup] chopped walnuts (optional)
    \item[1/2 cup] bittersweet chocolate (chips or chopped chunks) (optional)
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:10
    \item[Cook:]  00:18
    \item[Rest:]  00:15
    \item[Total:] 00:43
  \end{timeline}
\end{IT}

\begin{directions}
  \item Preheat oven to 425\degF.

  \item Whisk flour, baking powder, baking soda, and salt in medium bowl.

  \item Combine bananas, sugar, eggs, oil, and vanilla in large bowl and whisk
  until smooth. Add flour mixture and whisk until fully combined. Stir in the
  walnuts or chocolate chips if using.

  \item Bake in muffin tin until toothpick comes out clean, 14--18 minutes. Let
  muffins cool in muffin tin on a wire rack for 10 minutes, then remove muffins
  and let cool for an additional 5 minutes.
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Blueberry Muffins}{\CIBaking[42]} % {{{1
\index{Blueberry Muffins|see{\CIBaking[42]}}
\index{muffins!Blueberry Muffins|see{\CIBaking[42]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Carrot Cake}{\CIBaking[313]} % {{{1
\index{Carrot Cake|see{\CIBaking[313]}}
\index{cake!Carrot Cake|see{\CIBaking[313]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Chocolate Layer Cake}{\CIBaking[299]} % {{{1
\index{Chocolate Layer Cake|see{\CIBaking[299]}}
\index{cake!Chocolate Layer Cake|see{\CIBaking[299]}}
%---------------------------------------------------------------------------}}}1
\recipe{French Country Bread} \label{recipe:french_country_bread} % {{{1
\index{French Country Bread}
\index{bread!French Country Bread}

\begin{IT}[0.753]
  \begin{ingredients}[Biga Ingredients]
    \item[150 g] bread flour
    \item[30 g] whole wheat flour
    \item[1/2 tsp] instant yeast or active dry yeast
    \item[1 cup] water, 90--100\degF
  \end{ingredients}
  \begin{ingredients}[Bread Ingredients]
    \item[400 g] bread flour
    \item[13 g] sugar
    \item[2 tsp] salt
    \item[1/2 tsp] instant yeast or \textbf{3/4 tsp} active dry yeast
    \item[30 g] gluten (optional)
    \item[3/4 cup] water, 105--115\degF
  \end{ingredients}

  \switchcolumn

  \begin{timeline}[Biga Timeline]
    \item[Prep:]  00:05
    \item[Ferment:]  2:00 -- 16:00
  \end{timeline}
  \begin{timeline}[Bread Timeline]
    \item[Prep:] 00:30
    \item[Rise:] 1:30 -- 3:00
    \item[Cook:] 00:40
    \item[Total:] 2:40 -- 4:10
  \end{timeline}
\end{IT}

\begin{directions}
  \item Combine all biga ingredients, proofing the yeast in the water before
  adding it (if using non-instant). Cover with plastic wrap and let ferment
  2--16 hours (longer is better).

  \item Stir down the biga and combine with the bread ingredients, once again
  proofing the yeast in the water before adding it (if using non-instant). Stir
  until roughly incorporated, then let rest 15 minutes.

  \item After resting, knead the dough, adding enough flour for it to form a
  soft dough. Knead for 10 minutes.

  \item Let the dough rise in a lightly greased covered container until doubled
  in size, 45 minutes to 2 hours.

  \item Remove the dough from the container and gently form it into a round by
  flouring the counter and shaping it. Transfer to a lightly floured or
  cornmealed cloche or baking sheet. Cover and proof until 50\% larger, 30--90
  minutes. Preheat oven to 450\degF.

  \item Score the top of the bread and dust with flour. Bake at 450\degF for 35
  minutes in a covered cloche, then remove the cover and bake for an additional
  5. If using a baking sheet then bake for 40 minutes. Remove from oven and let
  cool on a rack.
\end{directions}
%----------------------------------------------------------------------------}}}1
\recipe{\^{G}ateau Invisible} \label{recipe:gateau_invisible} % {{{1
\index{\^{G}ateau Invisible}
\index{cake!\^{G}ateau Invisible}

\begin{IT}
  \begin{ingredients}
    \item[1/2 cup] sugar
    \item[2] eggs
    \item[1 Tbsp] vanilla extract
    \item[1/2 cup] flour
    \item[1 tsp] baking powder
    \item[1/2 tsp] salt
    \item[2.15--2.5 lbs] Granny Smith apples
    \itemNL honey or maple syrup
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:15
    \item[Cook:]  1:45
    \item[Cool:]  3:30
    \item[Total:] 5:30
  \end{timeline}
\end{IT}

\begin{directions}
  \item Combine sugar and eggs in large bowl and whisk until smooth. Whisk in
    flour, baking powder, and salt until smooth.

  \item Peel apples and slice 2.5mm thick on a mandolin. Reserve 18 well-shaped
    slices of apple for the top of the cake. Add remaining slices to the batter
    and fold gently to coat. Set aside for 15 minutes.

  \item Meanwhile, adjust oven rack to middle position and preheat to 350 \degF.
    Grease a loaf pan with vegetable oil spray, then line with parchment paper,
    cutting so that the narrow sides of the pan are uncovered on the inside and
    the longer sides have a couple inches of overhang. Finally, grease the
    parchment with vegetable oil spray.

  \item Stir apple mixture, breaking up clumps of slices as needed. Using a
    large slotted spoon, scoop apple slices into pan, letting excess batter
    drain back into the bowl and flattening the slices with the spoon.

  \item Dip one side of reserved slices in batter and shingle them,
    battered-side down, in 6 rows of 3 slices on the top of the cake. Press
    firmly on the apples with the back of a spoon to level and spread any
    remaining batter over the top of the cake.

  \item Place a baking sheet on a lower rack to catch any drippings.
    Bake for 1.5--1.75 hours, rotating pan halfway through baking, until top
    is browned and apples can be easily pierced with a skewer.

  \item Transfer to a wire rack, run a knife around narrow edge of pan, and
    brush top with honey or maple syrup. Let cool for 1.5 hours. After cooling,
    lift cake out of pan using the parchment paper as a sling. Let cool for an
    additional 2 hours.
\end{directions}
%---------------------------------------------------------------------------}}}1
\erecipe{Gingerbread Cake}{\CIBaking[264]} % {{{1
\index{Gingerbread Cake|see{\CIBaking[264]}}
\index{cake!Gingerbread Cake|see{\CIBaking[264]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Gingerbread Cookies}{\CICookbook[642]} % {{{1
\index{Gingerbread Cookies|see{\CICookbook[642]}}
\index{cookies!Gingerbread Cookies|see{\CICookbook[642]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Pumpkin Pie}{\CICookbook[720]} % {{{1
\index{Pumpkin Pie|see{\CICookbook[720]}}
\index{pie!Pumpkin Pie|see{\CICookbook[720]}}
%---------------------------------------------------------------------------}}}1
\recipe{Savory Dutch Baby} \label{recipe:savory_dutch_baby} % {{{1
\index{Savory Dutch Baby}
\index{dutch baby, savory}
\begin{IT}[0.727]
  \begin{ingredients}[Dutch Baby Ingredients]
    \item[1.75 cups (8.76 oz)] all-purpose flour
    \item[1 Tbsp] sugar
    \item[1/2 tsp] salt
    \item[1.5 cups] milk
    \item[6] eggs
    \item[3 Tbsp] butter
  \end{ingredients}

  \switchcolumn

  \begin{timeline}
    \item[Prep:]  00:20 (dutch baby) + 00:20 (topping)
    \item[Cook:]  00:35
    \item[Total:] 00:55
  \end{timeline}
\end{IT}

\begin{directions}[Dutch Baby Directions]
  \item Whisk flour, sugar, and salt together in large bowl. Whisk milk and eggs
  together in a second bowl. Whisk 2/3 of milk mixture into flour mixture until
  no clumps remain, then slowly whisk in remaining milk mixture until smooth.

  \item Adjust oven rack to lower-middle position. Melt butter in 12-inch
  nonstick skillet (or use cooking oil spray in traditional skillet) over
  medium-low heat. Add batter and transfer to cold oven. Set oven to 375\degF
  and bake until edges are deep golden brown and center is beginning to brown,
  30--35 minutes.

  \item While baking, prepare the topping (see below).

  \item Gently transfer to cutting board and let cool for at least 5 minutes
  before topping.
\end{directions}

\smallskip

\begin{twocols}
  \begin{ingredients}[Lox and Cucumber Ingredients]
    \item[1] shallot, small
    \item[1/4 tsp + 1/4 tsp] salt, divided
    \item[1/2 cup] sour cream
    \item[1 Tbsp] capers, plus \textbf{1 Tbsp} brine
    \item[1.5 tsp + 1.5 tsp] fresh dill, chopped, divided
    \item[1] English cucumber
    \item[8 oz] smoked salmon
  \end{ingredients}

  \begin{directions1col}[Lox and Cucumber Directions]
    \item Combine 1/2 cup water, shallot, and 1/4 tsp salt in a bowl and let sit
    for 5 minutes. Drain and discard liquid, setting shallot aside. Combine sour
    cream, caper brine, 1.5 tsp dill, and 1/4 tsp salt in a bowl.

    \item Shave cucumber using vegetable peeler lengthwise into ribbons until
    hitting seeds. Rotate 180\textdegree\ and repeat. Discard core.

    \item Spread sour cream mixture over Dutch Baby. Arrange salmon, then scatter
    cucumber ribbons, then sprinkle with shallot, capers, and 1.5 tsp dill.
  \end{directions1col}

  \columnbreak

  \begin{ingredients}[Mushroom and Red Pepper Ingredients]
    \item[2 Tbsp + 1 Tbsp] olive oil, divided
    \item[1.25 lbs] Portobello mushroom caps, gills removed, sliced thin
    \item[1/2 tsp + 1/4 tsp] salt, divided
    \item[1/2 tsp] lemon zest plus \textbf{2 tsp} lemon juice
    \item[1/4 tsp] sugar
    \item[1/2 cup] chopped roasted red peppers
    \item[2 oz] feta cheese, cut into 1/4 inch cubes
    \item[1/2 cup] parsley
    \item[1/4 cup] walnuts, chopped
  \end{ingredients}

  \begin{directions1col}[Mushroom and Red Pepper Directions]
    \item Heat 1 Tbsp oil in 12-inch pan over medium-high heat. Add mushrooms
    and 1/2 tsp salt and cook, stirring frequently, until tender, 4--6 minutes.

    \item Whisk lemon zest, juice, sugar, and 1/4 tsp salt. Whisking constantly,
    slowly add 2 Tbsp olive oil. Add red peppers, feta, and parsley and combine.

    \item Spread mushrooms over Dutch Baby, followed by red pepper mixture and
    walnuts.
  \end{directions1col}
\end{twocols}
%---------------------------------------------------------------------------}}}1
\erecipe{Tiramis\`u}{\CICookbook[700]} % {{{1
\index{Tiramis\`u|see{\CICookbook[700]}}
\index{cake!Tiramis\`u|see{\CICookbook[700]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Triple-Chocolate Mousse Cake}{\CIBaking[322]} % {{{1
\index{Triple-Chocolate Mousse Cake|see{\CIBaking[322]}}
\index{cake!Triple-Chocolate Mousse Cake|see{\CIBaking[322]}}
%---------------------------------------------------------------------------}}}1
\erecipe{Ultimate Chocolate Chip Cookies}{\CIScience[415]} % {{{1
\index{Ultimate Chocolate Chip Cookies|see{\CIScience[415]}}
\index{cookies!Ultimate Chocolate Chip Cookies|see{\CIScience[415]}}
%---------------------------------------------------------------------------}}}1

\chaptertoc{Miscellaneous} \label{chap:miscellaneous}
\recipe{Blackened Seasoning} \label{recipe:blackened_seasoning} % {{{1
\index{Blackened Seasoning}
\index{fish!Blackened Seasoning for}

\begin{ingredients}
  \item[2 Tbsp] paprika
  \item[1 Tbsp] cayenne
  \item[1 Tbsp] onion powder
  \item[1 tsp] garlic powder
  \item[1 tsp] black pepper
  \item[1 tsp] salt
  \item[1/2 tsp] dried basil
  \item[1/2 tsp] dried oregano
  \item[1/2 tsp] dried thyme
\end{ingredients}

\begin{directions}
  \item Mix all ingredients.
\end{directions}
%---------------------------------------------------------------------------}}}1
\recipe{Pan Sauces} \label{recipe:pan_sauces} % {{{1
\index{sauces, pan}

\begin{directions}[General Directions]
  \item After saut\'eing meat, tent loosely with foil. Add oil or butter to the
  pan if necessary and saut\'e the aromatics, no more than a couple minutes so
  as not to burn the fond, making it bitter.

  \item Add flour, if using, stirring constantly, for 30 seconds.

  \item Add final aromatics. Deglaze the pan with the liquids. If using wine,
  add wine first and reduce, then add other liquids and reduce. Return juices
  from tented meat to the pan.

  \item Off heat, add acids and butter. Season with salt and pepper to taste.
\end{directions}

\noindent\textbf{Ingredient lists yield two large servings.}

\begin{twocols}
  \begin{ingredients}[Garlic Lemon Thyme]
    \index{sauces, pan!Garlic Lemon Thyme}
    \item[1] shallot, minced
    \item[2] cloves garlic
    \itemNL fresh thyme
    \item[1 cup] chicken broth
    \item[1/2] lemon, juiced
    \item[1 Tbsp] butter
  \end{ingredients}

  \begin{ingredients}[Lemon Caper White Wine]
    \index{sauces, pan!Lemon Caper White Wine}
    \item[1] shallot, sliced thin
    \item[1.5 tsp (1/2 Tbsp)] capers, chopped
    \item[1/2 cup] white wine or vermouth
    \item[1/2 cup] chicken broth
    \item[1/2] lemon, juiced
    \item[1 Tbsp] butter
  \end{ingredients}

  \begin{ingredients}[Thyme Wine]
  \index{sauces, pan!Thyme Wine}
    \item[1] shallot, minced
    \itemNL fresh thyme
    \item[1/2 cup] wine (white or red)
    \item[1/2 cup] chicken stock
    \item[1 Tbsp] light brown sugar
    \item[1 Tbsp] butter
  \end{ingredients}

  \columnbreak

  \begin{ingredients}[Red Wine Rosemary]
    \index{sauces, pan!Red Wine Rosemary}
    \item[1] shallot, minced
    \itemNL fresh rosemary, chopped
    \item[1/2 cup] red wine
    \item[1/2 cup] chicken or beef broth
    \item[1 Tbsp] butter
  \end{ingredients}

  \begin{ingredients}[Red Wine Mushroom Thyme]
    \index{sauces, pan!Red Wine Mushroom Thyme}
    \item[4 oz] mushrooms, sliced thin (cook first, \about 5 min.)
    \item[1/2] shallot, minced
    \itemNL fresh thyme
    \item[1/2 cup] red wine
    \item[1/4 cup] chicken or beef broth
    \item[1/2 tsp] Dijon mustard
    \item[1.5 tsp] balsamic vinegar
    \item[1 Tbsp] butter
  \end{ingredients}

  \begin{ingredients}[Gravy]
  \index{sauces, pan!}
    \item[1 Tbsp] fat
    \item[1 Tbsp] flour
    \item[1 cup] broth or water
  \end{ingredients}

  % \begin{ingredients}[<++>]
  % \index{sauces, pan!}
  %   \item[<++>] <++>
  %   \item[<++>] <++>
  % \end{ingredients}
\end{twocols}
%---------------------------------------------------------------------------}}}1
\recipe{Rubs for Roasts} \label{recipe:rubs_for_roasts} % {{{1
\index{roasts, rubs for}

\begin{twocols}
  \begin{ingredients}[Garlic Rosemary Thyme Dijon]
    \index{roasts, rubs for!Garlic, Rosemary, Thyme, Dijon}
    \item[8] cloves garlic, minced
    \item[2 Tbsp] olive oil
    \item[2 Tbsp] fresh rosemary, chopped
    \item[2 Tbsp] fresh thyme, chopped
    \item[2 Tbsp] Dijon mustard
    \item[1 Tbsp] kosher salt
    \item[2 tsp]  black pepper
  \end{ingredients}

  \columnbreak

  \begin{ingredients}[Roasted Garlic Parsley]
    \index{roasts, rubs for!Roasted Garlic Parsley}
    \item[2 heads] garlic, roasted
    \item[2 Tbsp] parsley, minced
    \itemNL salt and pepper (on roast, after rub)
  \end{ingredients}

  \begin{ingredients}[Salt and Sugar]
    \index{roasts, rubs for!Salt and Sugar}
    \item[1/3 cup] brown sugar
    \item[1/3 cup] kosher salt
  \end{ingredients}
  \vspace{-0.75em} Rub, then cover the roast with plastic wrap and refrigerate
  for 12--24 hours.

  % \begin{ingredients}[<++>]
  %   \index{roasts, rubs for!<++>}
  %   \item[<++>] <++>
  %   \item[<++>] <++>
  % \end{ingredients}
\end{twocols}
%---------------------------------------------------------------------------}}}1

\backmatter
\def\thisrecipe{}  % clear recipe name
\pagenumbering[I]{bychapter} \printindex
\end{document}
